### 2014-05-31 writing/S'14 paper/intro.tex
Sketch of alternative intro

>>>>

\section{Introduction}\label{sec:intro}

Supervised recursive neural network models (RNNs) for sentence meaning
have been successful in a wide array of sophisticated language tasks,
including sentiment analysis, analogy completion, image description,
and paraphase detection. These results are encouraging about the
ability of these models to learn compositional semantic grammars, but
it remains an open question whether they can achieve the same results
as grammars based in logical forms when it comes to core semantic
concepts like quantification, entailment, and contradiction defined
over complex linguistic structures. These concepts are central to
robust natural language understanding, so it is essential that our
computational models be able to capture them.

We address this question directly by using a logical grammar to
generate controlled data sets encoding the semantic relationships
between pairs of expressions and evaluating whether each of two
classes of neural model --- plain RNNs and recursive neural tensor
networks (RNTNs) --- can learn those relationships correctly. Our
logical grammar is a version of the natural logic developed by
\cite{maccartney2009extended}, which defines seven core relations of
synonymy, entailment, contradiction, and mutual consistency. Natural
logic is well-suited to our purposes because of it defines a rich set
of relations between words, phrases, and sentences, and because its
logical expressions are derived directly from surface forms, making it
amenable to large-scale natural language processing.

In our first experiment, we show that both of these models can learn
the core relational algebra of natural logic from data. Our second
experiment builds on this result to cover relations between complex
recursive structures like `(A or B)' and `not(not A and not B)', and
our third experiment involves relations between quantified statements
like `every reptile walks' and `every turtle moves'. We find that the
plain RNN achieves only mixed results on the second and third
experiments, but that the stronger RNTN models generalized well in
every case, suggesting that it has in fact learned, or at least
learned to simulate, our target logical concepts.
